---
title: "p8105_hw5_al4225"
author: "Anjing"
date: "2022-11-16"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(broom)
library(dplyr)
knitr::opts_chunk$set(
  fig.width = 7,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Problem 2
### Raw data
**Describe the raw data.**    
In this raw dataset, it contains information about homicides in 50 large U.S. cities. There are `r homicide_data = read_csv("./data/homicide-data.csv",
                col_names = TRUE) %>%
  janitor::clean_names() 
  nrow(homicide_data)` observations and `r homicide_data = read_csv("./data/homicide-data.csv",
                col_names = TRUE) %>%
  janitor::clean_names()
  ncol(homicide_data)` variables. Some key variables such like victim_last, victim_first, victim_race, victim_age, victim_sex discribe victims' basic information about their name, race, age and sex. Some key variables such like reported_date, city, state, lat, lon describe the basic information about the date and location of homicides in U.S.. The variable disposition reflects the disposition of the murders.
```{r}
homicide_data = read_csv("./data/homicide-data.csv",
                col_names = TRUE) %>%
  janitor::clean_names() 
homicide_data
```
